\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}

\definecolor{limitblue}{RGB}{32, 76, 113}
\definecolor{ruddybrown}{rgb}{0.73, 0.4, 0.16}
\colorlet{punct}{red!60!black} 
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\definecolor{ogreen}{rgb}{0.0, 0.5, 0.0}
\colorlet{numb}{magenta!60!black}
 
\renewcommand\lstlistingname{Code}
\renewcommand\lstlistlistingname{Codes}
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
  language        = Python,
  frame           = lines, 
  basicstyle      = \footnotesize,
  keywordstyle    = \color{blue},
  stringstyle     = \color{green},
  commentstyle    = \color{red}\ttfamily
}
\lstdefinestyle{R}{
  language        = R,
  frame           = lines,
  captionpos      = b,
  abovecaptionskip= 10pt, 
  emphstyle       = \textbf,
  framextopmargin = 4pt,
  framexbottommargin = 4pt,
  basicstyle      = \ttfamily\footnotesize,
  keywordstyle    = \color{limitblue},
  stringstyle     = \color{ruddybrown},
  showstringspaces= false,
  commentstyle    = \color{red}\ttfamily,
  tabsize         = 2,
  literate=
    *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1}
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{Statistics I}
\newcommand\hwnumber{8.2}                  % <-- homework number
\newcommand\NetIDa{Atreya Choudhury}           % <-- NetID of person #1
\newcommand\NetIDb{bmat2005}           % <-- NetID of person #2 (Comment this line out for problem sets)

\pagestyle{fancyplain}
\headheight 35pt
\lhead{\NetIDa}
\lhead{\NetIDa\\\NetIDb}                 % <-- Comment this line out for problem sets (make sure you are person #1)
\chead{\textbf{\Large Assignment \hwnumber}}
\rhead{\course \\ \today}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 2em

\begin{document}
\textit{A garment manufacturing company recorded the amount of time that it took to make a pair of jeans on 8 different occasions. The times in minutes are listed below. Assume these measurements were taken from a population with a normal distribution. The company claims that the average time is not more than 11 minutes and we want to test this claim.}
$$12.5, 13.0, 11.9, 10.2, 13.1, 13.6, 13.8, 14.0$$

\begin{enumerate}[a.] \setlength{\itemsep}{30pt}
  \item State the appropriate hypotheses.
  
  \textbf{Solution:}
  The null hypothesis is that the average time to make a pair of jeans is 11 minutes and the alternative hypothesis is that the average time to make a pair of jeans is more than 11 minutes.

  $H_0$ : $\mu = 11$\\
  $H_a$ : $\mu > 11$
  \item Compute the test statistic for the hypotheses in part (a).

  \textbf{Solution:}
  The test statistic is given by

  \begin{equation}
    \begin{split}
      t &= \frac{\overline{x} - \mu}{\frac{s}{\sqrt{n}}}\\
      \implies t &\approx 4.003
    \end{split}
  \end{equation}

  \item Does the sample data support the alternative hypothesis at the 5\% level?

  \textbf{Solution:}
  The p-value associated with the test statistic is given by

  \begin{equation}
    \begin{split}
      p &= \mathbb{P}(t > 4.003)\\
      \implies p &\approx 0.003
    \end{split}
  \end{equation}

  $\because \alpha = 0.05 > 0.003,$ we reject the null hypothesis.

  The sample data supports the alternative hypothesis at the 5 \% level.
  \end{enumerate}
\newpage
\lstinputlisting[language=R, style=R, title=R Code]{code.R}
\end{document}